Are we living in a depressive society?

### 2024-04-03 outputs/paper/paper.qmd
commite

# Plotting the line graph
ggplot(filtered_data, aes(x = Time.Period.End.Date, y = Value, group = Indicator, color = Indicator)) +
  geom_line() +
  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  # Set specific dates as x-axis breaks
  labs(x = "Date",
       y = "Symptom Rates (%)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        plot.margin = unit(c(1, 1, 1, 1), "cm"))

@@

Both Anxiety and Depressive Disorder showing the similar trends over the period. 
## Trends in Anxiety and Depressive Disorder Rates by Population Subgroup

@@

# Filter the dataset for the specified symptoms
filtered_data <- data %>%
  filter(Indicator == "Symptoms of Depressive Disorder")  # Assuming you need only this indicator

# Ensure that 'Time Period End Date' is a Date object
# Make sure to use the exact column name as it appears in your CSV file, including using backticks if necessary
filtered_data$`Time Period End Date` <- as.Date(filtered_data$`Time Period End Date`, format = "%Y-%m-%d")

@@

# Plotting the line graph
ggplot(filtered_data, aes(x = `Time Period End Date`, y = Value, group = Subgroup, color = Subgroup)) +
  geom_line() +
  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  
  labs(x = "Date",
       y = "Symptom Rates (%)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        plot.margin = unit(c(1, 1, 1, 1), "cm"))

>>>>

# Plotting the line graph
ggplot(filtered_data, aes(x = Date, y = Value, group = Indicator, color = Indicator)) +
  geom_line() +
  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  # Set specific dates as x-axis breaks
  labs(x = "Date",
       y = "Symptom Rates (%)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        plot.margin = unit(c(1, 1, 1, 1), "cm"))

@@

Both Anxiety and Depressive Disorder showing the similar trends over the period.

## Trends in Anxiety and Depressive Disorder Rates by Population Subgroup

@@

# Filter the dataset for the specified symptoms
filtered_data <- data %>%
  filter(Indicator == "Symptoms of Depressive Disorder")

@@

# Plotting the line graph
ggplot(filtered_data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
  geom_line() +
  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  
  labs(x = "Date",
       y = "Symptom Rates (%)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        plot.margin = unit(c(1, 1, 1, 1), "cm"))
